%----------------------------------------------------------------------------------------
% ATS-FRIENDLY RESUME - DEVARANGAREDDY D
% Clean, 2-page, ATS-optimized LaTeX resume
%----------------------------------------------------------------------------------------

\documentclass[9.5pt, letterpaper]{article}

% PACKAGES
\usepackage[top=0.4in, bottom=0.4in, left=0.55in, right=0.55in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{parskip}

% HYPERLINK SETUP
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=black}

% SECTION FORMATTING
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{3pt}

% LIST FORMATTING
\setlist[itemize]{leftmargin=1.2em, topsep=1pt, itemsep=0pt, parsep=0pt}

% NO PARAGRAPH INDENT
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
% HEADER
%----------------------------------------------------------------------------------------
\begin{center}
    {\LARGE \textbf{DEVARANGAREDDY D}} \\[4pt]
    \href{mailto:devarangareddy.dande@gmail.com}{devarangareddy.dande@gmail.com} \quad | \quad
    +91-9849393806 \quad | \quad
    Hyderabad, India
\end{center}

%----------------------------------------------------------------------------------------
% PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------
\section{Professional Summary}

Results-driven Full Stack / Frontend Developer with \textbf{8+ years of IT experience} in designing and developing scalable web and enterprise applications. Proficient in \textbf{Angular, React JS, JavaScript, HTML5, CSS3, Bootstrap, and jQuery}. Experienced in SCADA/Ignition development, IoT solutions, AWS cloud services, and DevOps practices. Proven ability to deliver high-performance, user-centric applications across industrial automation, transportation, and IoT domains.

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}

\begin{tabular}{@{}p{2.2in} p{4.2in}}
\textbf{Frontend} & Angular, React JS, HTML5, CSS3, JavaScript, jQuery, Bootstrap, AJAX \\[2pt]
\textbf{Programming Languages} & Java, JavaScript, Python \\[2pt]
\textbf{SCADA / Industrial} & Ignition SCADA, Ignition Perspective, UDTs, Tag Historian \\[2pt]
\textbf{Backend / Frameworks} & Spring, Struts, Hibernate, Servlets, JSP, Web Services \\[2pt]
\textbf{Cloud (AWS)} & EC2, VPC, ELB, S3, RDS, EBS \\[2pt]
\textbf{Databases} & Oracle, MySQL, SQL, JDBC \\[2pt]
\textbf{DevOps \& Tools} & Git, Maven, Gradle, Docker, SonarQube, Jira, SVN, Log4j \\[2pt]
\textbf{Web Servers} & Apache Tomcat, WebLogic, WebSphere \\[2pt]
\textbf{IDE / OS} & Eclipse, Windows, Linux \\[2pt]
\textbf{Testing} & JUnit, HttpUnit, Postman (GET/POST APIs), UAT Testing \\
\end{tabular}

%----------------------------------------------------------------------------------------
% PROFESSIONAL EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Professional Experience}

\textbf{Software Developer} \hfill Nov 2020 -- Present \\
\textit{Cyient Limited, Hyderabad}

\textbf{Software Engineer} \hfill Apr 2018 -- Oct 2020 \\
\textit{Seaton India IT Pvt. Ltd}

\textbf{Software Engineer} \hfill Aug 2016 -- Mar 2018 \\
\textit{HCL Technologies}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section{Key Projects}

%--- Project 4 ---%
\textbf{SCADA Upgradation} \hfill Jan 2024 -- Present \\
\textit{Client: INFRAMARK | Cyient Limited} \\
\textit{Environment: Ignition SCADA, Ignition Perspective, Python, Angular, React JS, Oracle}

\begin{itemize}
    \item Designed and developed \textbf{Ignition Perspective applications} with responsive WUI dashboards featuring \textbf{2D and 3D visualizations} for real-time monitoring and control.
    \item Implemented \textbf{Python scripting} for application logic, event handling, alarm processing, and real-time data operations.
    \item Created and maintained \textbf{Ignition tag structures} (UDTs) and configured \textbf{Tag Historian} for historical process data storage and analysis.
    \item Integrated \textbf{Oracle/MySQL databases} for alarms, events, and reporting functionalities.
    \item Built responsive interfaces using \textbf{HTML, CSS, Bootstrap, JavaScript, React JS, and Angular} for enhanced user interaction.
    \item Used \textbf{AJAX and jQuery} for asynchronous data communication and dynamic UI updates.
    \item Collaborated with stakeholders to gather requirements and deliver scalable industrial automation solutions.
\end{itemize}

\vspace{2pt}

%--- Project 3 ---%
\textbf{PW Asheville -- Shop Floor Management Tools (Andon System)} \hfill Jan 2023 -- Dec 2023 \\
\textit{Client: PWA USA | Cyient Limited} \\
\textit{Environment: Angular, React JS, Python, Ignition SCADA, Oracle, MySQL}

\begin{itemize}
    \item Designed a \textbf{shop-floor Andon application} using Ignition SCADA, React JS, and Python to provide real-time machine status and production visibility.
    \item Developed responsive web-based dashboards using \textbf{Angular, React JS, HTML, Bootstrap, CSS, and JavaScript} to display real-time production metrics.
    \item Implemented \textbf{AJAX and jQuery} for asynchronous data fetching and dynamic UI updates.
    \item Integrated front-end with backend services using \textbf{Java and Python} for real-time data communication and event processing.
    \item Designed \textbf{MySQL database queries} for event logging, downtime tracking, and historical reporting.
    \item Used \textbf{Git} for version control; performed testing, deployment, and production support.
\end{itemize}

%----------------------------------------------------------------------------------------
% PAGE 2
%----------------------------------------------------------------------------------------
\newpage

%--- Project 2 ---%
\textbf{IoT Platform (Cloud Platform \& IoT Gateway)} \hfill May 2022 -- Oct 2022 \\
\textit{Client: Cyient Ltd.} \\
\textit{Environment: Angular, React JS, AJAX, JavaScript, jQuery, HTML, Bootstrap, CSS, Java, Python, MySQL}

\begin{itemize}
    \item Developed UI for an \textbf{IoT Cloud Platform and Gateway} application enabling wired and wireless connectivity to sensors via multiple protocols (USB, RS-232/485, SPI, I2C, GSM, GPRS).
    \item Designed front-end components using \textbf{Angular, React JS, HTML, Bootstrap, CSS, and JavaScript} for the IoT monitoring dashboard.
    \item Implemented \textbf{Python scripting} for data collection, collation, and end-to-end business logic at the IoT device level.
    \item Used \textbf{Git} for source control and collaborated with cross-functional teams for agile delivery.
\end{itemize}

\vspace{2pt}

%--- Project 1 ---%
\textbf{UMB -- Urban Mobility Backoffice (Revenue Management System)} \hfill Nov 2020 -- Feb 2022 \\
\textit{Client: Cubic Transportation Systems (India) Pvt. Ltd. | Cyient Limited} \\
\textit{Environment: HTML5, CSS3, Bootstrap, Angular JS/2x, JavaScript, AJAX, jQuery, AWS, DevOps, Maven, Log4J, SQL}

\begin{itemize}
    \item Designed and developed application UI using \textbf{HTML5, CSS3, Bootstrap, Angular JS (1.x, 2.x), JavaScript, jQuery, and AJAX}.
    \item Created \textbf{notification templates} (ticket confirmation emails) using HTML5 and stored templates in the database.
    \item Managed deployment, automation, and maintenance of \textbf{AWS cloud-based production systems} ensuring availability, performance, security, and scalability.
    \item Implemented \textbf{JSP forms and navigation} using View Resolver; developed business logic and integrated dynamic pages with static designs.
    \item Performed \textbf{code reviews and UAT testing}; managed SVN repository and coordinated release management.
    \item Used \textbf{Maven, Log4J, and JUnit} for build management, logging, and unit testing.
\end{itemize}

\vspace{2pt}

%--- Seaton India ---%
\textbf{Frontend / Full Stack Developer} \hfill Apr 2018 -- Oct 2020 \\
\textit{Seaton India IT Pvt. Ltd}
\begin{itemize}
    \item Developed web applications using \textbf{Angular, React JS, HTML5, CSS3, Bootstrap, JavaScript, and jQuery}.
    \item Worked on \textbf{DevOps} operations, version control with \textbf{Git}, and CI/CD pipelines.
    \item Integrated REST APIs using \textbf{Postman} and managed SQL databases for data persistence.
    \item Implemented MVC architecture and deployed applications on \textbf{Apache Tomcat} server.
\end{itemize}

\vspace{2pt}

%--- HCL ---%
\textbf{Software Engineer} \hfill Aug 2016 -- Mar 2018 \\
\textit{HCL Technologies}
\begin{itemize}
    \item Built enterprise web applications using \textbf{Java, Spring, Hibernate, HTML, CSS, and JavaScript}.
    \item Deployed WAR files on \textbf{Apache Tomcat, WebLogic, and WebSphere} application servers.
    \item Performed code quality analysis with \textbf{SonarQube} and managed builds with \textbf{Maven/Gradle}.
    \item Used \textbf{Docker} to create images and containers for application deployment.
    \item Monitored application logs for exceptions and performance issues.
\end{itemize}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\textbf{Master of Computer Applications (MCA)} \\
Jawaharlal Nehru Technological University (JNTU)

%----------------------------------------------------------------------------------------
% ADDITIONAL HIGHLIGHTS
%----------------------------------------------------------------------------------------
\section{Additional Highlights}

\begin{itemize}
    \item Experienced in \textbf{AWS} services: EC2, VPC, ELB, S3, RDS, EBS for cloud-based deployments.
    \item Proficient in \textbf{Docker} -- creating and managing Docker Images and Containers.
    \item Good understanding of \textbf{unit testing} and code quality tools like \textbf{SonarQube, JUnit, and HttpUnit}.
    \item Strong knowledge of \textbf{MVC design architecture} and agile development methodologies.
    \item Self-motivated team player with a positive attitude, quick learner, and eager to adopt new technologies.
\end{itemize}

\end{document}
